---
title: "DSCI353-353m-453: Class 0b-p Bash Git BitBucket"
subtitle: "2001-353-353m-453-01b-p-BashGitBitBucket"
author: "Roger H. French, Peitian Wang"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    toc: true
    number_sections: true
    toc_depth: 6
    highlight: tango
  html_document:
    toc: yes
urlcolor: blue
---

 \setcounter{section}{1}
 \setcounter{subsection}{2}
 \setcounter{subsubsection}{2}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width = 6, fig.height = 4.5) 
```
 
 <!-- 
 How to make comments inside Rmarkdown
-->

<!-- Or on a single line like this -->
 
 
### R Learning Resources  

  * Peng: R Programming for Data Science (Book, in readings)
  * Roger Peng's [Youtube Playlist for 4 weeks of Coursera R Programming](https://www.youtube.com/playlist?list=PLjTlxb-wKvXNSDfcKPFH2gzHGyjpeCZmJ)
  
  
### SDLE Teatime Learning

  - 2016 year was intro to datascience, R, Python, Git, LaTeX
  - 2017 was more advanced topics including Hadoop and Spark and SparklyR
  - 2018 continued with more advanced topics and review
  
#### SDLE TeaTime Learnings Materials are available Online

  - [2018 SDLE Teatime Repo](https://bitbucket.org/cwrudsci/18-sdle-teatime/)
    - 2018 contains the prior years code
    - [2016 SDLE Teatime Repo](https://bitbucket.org/cwrudsci/16-sdle-teatime) 
    - [2017SDLE Teatime Repo](https://bitbucket.org/cwrudsci/17-sdle-teatime) 
  - [SDLE Teatime Youtube Videos and Playlists](https://www.youtube.com/channel/UCer8o-Bxh-xef_6Kdmq4Kvg/videos)
 
```{r,echo=FALSE,message=FALSE}
options("digits" = 5)
options("digits.secs" = 3)
```

#### What we need setup by now for class

  1. [Setup Data Science Slack for class](http://cwru-dsci.slack.com)
    - Use case.edu email address
  2. [Setup Bitbucket Account](http://bitbucket.org)
    - Use case.edu email address
  3. Setup VDI
   - Rstudio
   - Drag icons of R, Rstudio, Git Bash, Spyder, Jupyter Notebook, Slack to desktop 
   - Slack client on ODS VDI
   - Can put slack app on phone, or on your notebook
  4. Setup Git
  
    - make H:\\Git folder 
    - git config name and email
  5. Setup StackExchange
  6. [Setup Kaggle.com account](http://kaggle.com)
    - Use your caseID email as a google account for login
  7. Setup CWRU HPC Data Science Cluster Account
    - I'll provide more information shortly
  8. Git Clone
    - For Class-Prof Repo
      - Fork the prof repo up on bitbucket
        - remove `-prof` and rename your student repo with your `-caseID`
      - Clone your fork of the Prof Class Repo
        - Down onto your ODS VDI's H: drive in the `H:/Git/` folder
    - For those "new to R" 18-sdle-tea-time
      - for quick introduction to data science techniques and tools
      - `git clone git@bitbucket.org:cwrudsci/18-sdle-teatime.git`


### Some students may not have forked the class repo?

  - [DSCI-353-353m-453 group in CWRU-DSCI team](https://bitbucket.org/account/user/%7B85cf8671-ad4f-4916-9caf-e32631f870b4%7D/groups/19su-tu-itfun-adswr/)
 
### Bash: The language of the Linux Console 
 
  * Bash is the command line processor of the Linux Console
  * R has its own command line processor for the R Console
  * Bash is the default Console for both Linux and for Mac
    + Mac's are based on BSD-Unix OS
    + A close variant of Linux, only different by the licensing
  * Windows uses the DOS command line processor in its 'Command Prompt'

 
#### On our ODS VDI's we use Git Bash to work with Git

  * MinGW64 is a little Linux OS running inside Windows
    + It has the standard Bash commands
    + And tools like vim (the visual text editor)
    
#### Lets see some Bash Commands we'll be using

  * `ls` is the "list" command, to get a directory of files and folders
  * `pwd` is the "present working directory" command, to know where you are
  * `cd` is "change directory" 
  * `..` refers to the directory one up from where you are
  * so `cd ..` moves you up one directory
  * and `cd Downloads` would move you down into Downloads directory (if it exists)
  * To copy a file use `cp`
  * To move a file use `mv`  
  * To make a new directory use `mkdir`
    
#### A good resource for Bash Commands and Man pages

  * Is [An A-Z Index of the Bash command line for Linux](http://ss64.com/bash/)
  * There are many other resources too

### Now lets start working with our local Git Server

  * Using Git Bash to talk to it
    * Git is also a linux program 
  * All Git commands are entered at the Bash Prompt
  * All Git commands start with `git`
  * So that the Bash prompt know who to send the subsequent command to
    
##### Check your Git Server Configuration
          
          `git config --list`

##### Essential `git config --global`'s, Set your user info

  - `git config --global user.name "[name]"`
  - `git config --global user.email "[email address]"`
  - `git config --global color.ui auto`

#### First we need to go up to Bitbucket and "Fork" the Prof. Repo

  * This will give you a copy of Prof. Repo
    * In your personal account area
    * You want to change the ending from "Prof" to your caseID
    
#### Now you want to open Git Bash on Windows

  * You need to save your Repos on your H: drive, NOT C drive
    * C Drive is restricted
    * H Drive is your personal area that follows your caseID login
  * So in Git Bash
    * `pwd` will tell you your present working directory
    * `cd ..` moves up a directory
    * `pwd` to see where you have moved
    * Now change to H: `cd /h`
    * `pwd` see where you are
    * `ls` see what files are there
    * `mkdir Git`  this will make a new directory at H:Git
      + So you'll keep all your repositories under H:Git 

#### Important Note: **Windows ignores case, Linux and BSD-Unix (Mac) respect case**

  * So Git and git are the same on windows for a folder
  * They are totally different on Linux or Mac
  * Best practice Use capitals sparingly
  * About only useful place is in CamelBack filenames
    * Since I said, no spaces in filenames
    * To make things readable, you can do CamelBack
    * Example: 1906ITFun-ADSwR-ThisIsMyReport-Name.rmd
    
### Now lets Clone your personal class repo    
    
  * Now you want to Clone your personal class repo
    * This is a one time operation
    * To copy all the files and folders down to your local computer
  * In Git Bash, you want to be at H:Git or h:Git
    Check with `pwd`
  * Now go to your personal class repo on Bitbucket
    * And find the clone command
    * **For windows choose https protocol (Not ssh)**
  * Copy the command
    * Its something like this 
    * `git clone https://vuvlab@bitbucket.org/cwrudsci/20s-dsci353-353m-453-prof.git`
  * Now that that is on your clipboard
  * Go to you Git Bash, and use "Shift-Insert" (Not "Cntrl-v")
    * To copy it onto the Bash Command line
    * Hit enter, and watch a full copy of your repo being copied locally
    
### For class repos

  - Before each class, or whenever you want
  - Up on Bitbucket
    - You should sync your fork
    - With my Prof repo
    - To get the latest file version and new files
    - After syncing
    - Now `git pull` to bring the updated files to your local git server

### Now lets pull and push changes from to your repo

  * cd into your repo's top folder
    * This can be done with tab completion
    * `cd 20s-d ` and hit tab, it auto completes
  * Now type `git pull` To see if there are any changes up on bitbucket
    And to pull these down and merge them in

### Making local changes, Adding, Commmitting and Pushing

  * Now change a local file by adding something into it
  * Now you add this changed file to be tracked by Git
    * `git add --all :/` 
  * Now commit your changes
    * `git commit -m 'I have changed the readme.md' `
  * Now push your changes up to Bitbucket, to your personal repo
    * `git push`
    
### Links
 
  - https://www.r-project.org 
  - https://help.ubuntu.com/community/UsingTheTerminal
  
  


